Haskell in Computational Biology

### 2013-05-25 jfp.tex
tinking with end of sectino 3 intro

The model in \figref{plan7} is from a well-established family
that permits
transitions between match states and all other adjacent states,
but forbids
direct
transitions between insertion 
states and deletion states  \cite{Eddy:1998ut}. 
The family is called the ``Plan7'' family because
every model in the family has 7~transitions per node.
Each transition has its own probability; the probabilities for
transitions leaving states in node~$j$ are
$\txprobjj I I$,
$\txprobxj I M$,
$\txprobjj M I$,
$\txprobxj M M$,
$\txprobxj M D$,
$\txprobxj D M$,
and
$\txprobxj D D$.
When column $j+1$ is a consensus column, the transitions that enter
its match state 
($\txprobxj I M$,
$\txprobxj M M$,
$\txprobxj D M$)
are more likely.
When column $j+1$ is a non-consensus column, the transitions that enter
its insertion and deletion states are more likely.

>>>>

The model in \figref{plan7} is from a well-established family
that permits
transitions between match states and all other adjacent states,
but forbids
direct
transitions between insertion 
states and deletion states  \cite{Eddy:1998ut}. 
The family is called the ``Plan7'' family because
every model in the family has 7~transitions per node.
Each transition has its own probability; the probabilities for
transitions leaving states in node~$j$ are
$\txprobjj I I$,
$\txprobxj I M$,
$\txprobjj M I$,
$\txprobxj M M$,
$\txprobxj M D$,
$\txprobxj D M$,
and
$\txprobxj D D$.
(The transitions from match to insertion and from insertion to
insertion leave states in 
node~$j$ but also enter states in node~$j$.
The other transitions enter states in node~$j+1$.)
When column $j+1$ is a consensus column, the transitions that enter
its match state 
%($\txprobxj I M$,
%$\txprobxj M M$,
%$\txprobxj D M$)
are more likely.
When column $j+1$ is a non-consensus column, the transitions that enter
its insertion and deletion states are more likely.
